### 2021-05-23 paper/NIHGrant.tex
Add new figures, section on VAEs/manifold

\begin{table}[h]
	\myfloatalign
	\begin{tabularx}{\textwidth}{>{\raggedright}p{35mm} >{\raggedright\arraybackslash}p{40mm} >{\raggedright\arraybackslash}p{45mm} >{\raggedright\arraybackslash}p{50mm}}
		\toprule
		\textbf{Approach} & \textbf{Stimulus} & \textbf{Measurements} & \textbf{Output} \\ [0.5ex] 
		\rowcolor{Gray} Forced selection & Constructed stimuli, constrained variation & Subjective choice & Representation with \newline defined acoustic properties \\
		Likeness measures & Constructed stimuli, constrained variation & Subjective ratings & Frequency spectra \\
		\rowcolor{Gray} Neural monitoring & N/A & Neural signals (\eg fMRI) & Correlation maps in localized brain regions, functional connectivity maps \\
		\textbf{Reverse Correlation} & Constructed stimuli, unconstrained variation & Response classification (\eg present/absent) & Representations best explaining classification behavior \\
		\bottomrule
	\end{tabularx}
	\caption[Approaches]{Comparison of approaches for estimating cognitive representations.
	Each approach has benefits and limitations regarding stimuli, measurements, and output.
	The proposed approach, featured in the final row, is the only approach that can directly
	uncover a time-frequency map of the cognitive representation that best explains tinnitus percepts.}
	\label{tab:approaches}
\end{table}

We propose to implement a reverse correlation
approach for recovering cognitive representations of speech which allows for unconstrained, direct
characterization of latent representations from yes-no responses to randomly-generated stimuli.
Participants will be asked to classify random auditory stimuli as containing or not containing their tinnitus percept.
This is a transductive task that we model as comparing a stimulus to a latent ``cognitive template'' in a top-down process
(\autoref{fig:template}).
The latent representation that drives that top-down process
can then be estimated by regressing observed responses against the stimuli over many trials \cite{mineaultImprovedClassificationImages2009}.
We use random stimuli in order to sample the space of percepts without biasing towards any particular representation, a problem with other approaches.

\begin{figure}[h] % Figure at bottom of the page ([b] argument, could be "t" for top or "h" for here)
	\centering
	\includegraphics[width=0.8\textwidth]{Figures/Figures_tinnitus_1.png}
	\caption{Model of the discrimination task as a transductive process.
	Random stimuli is filtered by the subject using low-level sensory mechanisms.
	The perceptual discrimination task however is a top-down process that
	compares the sensory information to a perceptual representation ``template''
	to determine if the stimulus belongs to that perceptual representation.}
	\label{fig:template}
\end{figure}

@@

\begin{figure}[h] % Figure at bottom of the page ([b] argument, could be "t" for top or "h" for here)
	\centering
	\includegraphics[width=0.8\textwidth]{Figures/Figures_tinnitus_3.png}
	\caption{Schematic overview of experiments proposed in Aim \#1.
	Simulation results are shown, demonstrating proof-of-concept
	for the proposed reverse correlation paradigm.}
	\label{fig:experiment}
\end{figure}

@@

We propose to develop an advanced signal processing pipeline
that will enable us to overcome the inefficiencies of existing reverse correlation methods
through the use of \emph{compressive sensing},
a recent advance in signal processing which has led to dramatic improvements in efficiency
over conventional sampling and signal estimation methods
\cite{baraniukCompressiveSensingLecture2007}.
Compressive sensing has recently gain wide recognition in domains such as medical imaging
\cite{graffCompressiveSensingMedical2015,lustigCompressedSensingMRI2008},
where considerations of efficiency and bias reduction are critical.
Compressive sensing holds promise to similarly improve the efficiency of reverse correlation
without the drawback of biasing estimates.
Compressive sensing will extend the range of possible cognitive and perceptual mechanisms that can be estimated
by dramatically decreases the number of trials needed for signal reconstruction.
Since compressive sensing can be directly substituted for conventional, regression-based estimation,
it can be directly substituted into eixsting experimental protocols without requiring other changes.
Our ultimate objective is to develop and validate a compressive sensing
data processing pipeline – culminating in an open-source software tool – that will allow for
efficient and accurate reconstruction of latent representations using data 
obtained via the reverse correlation method.

@@

\begin{figure}[h] % Figure at bottom of the page ([b] argument, could be "t" for top or "h" for here)
	\centering
	\includegraphics[width=\textwidth]{Figures/CompSensExamples.pdf}
	\caption{Compressive sensing (CS) delivers accurate signal reconstruction from sampling
	with a comparatively small number of samples.
	The latent representation in \emph{A} is estimated in \emph{B-E}.
	In \emph{B-C} conventional regression-based estimation is used
	and in \emph{D-E} compressive sensing is used.
	The number of samples $n$ is displayed along with the correlation coefficient $r^2$
	between the estimated reconstruction and the original signal,
	as a measure of reconstruction quality.}
	\label{fig:csexample}
\end{figure}

@@

We will perform a quantitative analysis based on latent variable analysis methods.
Latent variable methods relate observed variation (\eg in tinnitus representations)
to latent variables that capture the observed variation (\eg major variation types across tinnitus percepts).
We will use principle component analysis (PCA), t-stochastic neighbor embedding (t-SNE; \cite{vandermaatenBarnesHutSNE2013}),
and uniform manifold approximation and projection (UMAP; \cite{mcinnesUMAPUniformManifold2020}).
Applying these dimensionality-reduction algorithms to a collection of representations
will identify major modes of variation across those representations,
and, in the case of PCA, provide an analysis of the proportion of variance explained by each mode
(the PCA eigenvalues).
Clusters of data points become readily visible in the lower-dimensional manifold generated
by these unsupervised machine learning methods, each of which represents
a data-driven tinnitus subtype.
We will characterize these subtypes, identifying their properties and assigning them descriptive names.
In the case of PCA and UMAP, new data can be mapped into the lower-dimensional manifold,
allowing representations from new subjects to be classified into these subtypes.

>>>>

\begin{table}[h]
	\myfloatalign
	\begin{tabularx}{\textwidth}{>{\raggedright}p{35mm} >{\raggedright\arraybackslash}p{40mm} >{\raggedright\arraybackslash}p{45mm} >{\raggedright\arraybackslash}p{50mm}}
		\toprule
		\textbf{Approach} & \textbf{Stimulus} & \textbf{Measurements} & \textbf{Output} \\ [0.5ex] 
		\rowcolor{Gray} Forced selection & Constructed stimuli, constrained variation & Subjective choice & Representation with \newline defined acoustic properties \\
		Likeness measures & Constructed stimuli, constrained variation & Subjective ratings & Frequency spectra \\
		\rowcolor{Gray} Neural monitoring & N/A & Neural signals (\eg fMRI) & Correlation maps in localized brain regions, functional connectivity maps \\
		\textbf{Reverse Correlation} & Constructed stimuli, unconstrained variation & Response classification (\eg present/absent) & Representations best explaining classification behavior \\
		\bottomrule
	\end{tabularx}
	\caption[Approaches]{Comparison of approaches for estimating cognitive representations.
	Each approach has benefits and limitations regarding stimuli, measurements, and output.
	The proposed approach, featured in the final row, is the only approach that can directly
	uncover a time-frequency map of the cognitive representation (a spectrogram) that best explains tinnitus percepts.}
	\label{tab:approaches}
\end{table}

We propose to implement a reverse correlation
approach for recovering cognitive representations of speech which allows for unconstrained, direct
characterization of latent representations from yes-no responses to randomly-generated stimuli.
Participants will be asked to classify auditory stimuli,
which vary in their time-frequency content, as containing or not containing their tinnitus percept.
This is a transductive task which we model as comparing a stimulus to a latent ``cognitive template'' in a top-down process
(\autoref{fig:template}).
The latent representation that drives that top-down process
can then be estimated by regressing observed responses against the stimuli over many trials \cite{mineaultImprovedClassificationImages2009}.
We use random stimuli,
\ie stimuli where the frequency magnitudes are randomly chosen, in order to sample the space of percepts without biasing towards any particular representation, a problem with other approaches.
We will consider both time-varying and stationary stimuli, \ie where the spectral content of the stimuli changes over time and where it remains constant.

\begin{figure}[h] % Figure at bottom of the page ([b] argument, could be "t" for top or "h" for here)
	\centering
	\includegraphics[width=0.8\textwidth]{Figures/Figures_tinnitus_1.png}
	\caption{Model of the discrimination task as a transductive process.
	Random stimuli is filtered by the subject using low-level sensory mechanisms.
	The perceptual discrimination task is modeled as a top-down process that
	compares the sensory information to a perceptual representation ``template''
	to determine if the stimulus belongs to that perceptual representation.}
	\label{fig:template}
\end{figure}

@@

\begin{figure}[h] % Figure at bottom of the page ([b] argument, could be "t" for top or "h" for here)
	\centering
	\includegraphics[width=0.8\textwidth]{Figures/Figures_tinnitus_3.png}
	\caption{Schematic overview of experiments proposed in Aim \#1.
	Subjects are presented with random stimuli,
	which is compared to a latent internal representation.
	Reverse correlation is used to reconstruct the latent internal representation
	from many trials.
	Simulation results are shown, demonstrating proof-of-concept
	for the proposed reverse correlation paradigm.}
	\label{fig:experiment}
\end{figure}

@@

We propose to develop an advanced signal processing pipeline
that will enable us to overcome the inefficiencies of existing reverse correlation methods
through the use of \emph{compressive sensing},
a recent advance in signal processing which has led to dramatic improvements in efficiency
over conventional sampling and signal estimation methods
\cite{baraniukCompressiveSensingLecture2007}.
Compressive sensing has recently gain wide recognition in domains such as medical imaging
\cite{graffCompressiveSensingMedical2015,lustigCompressedSensingMRI2008},
where considerations of efficiency and bias reduction are critical.
Compressive sensing holds promise to similarly improve the efficiency of reverse correlation
without the drawback of biasing estimates.
Compressive sensing will extend the range of possible cognitive and perceptual mechanisms that can be estimated
by dramatically decreases the number of trials needed for signal reconstruction.
Since compressive sensing can be directly substituted for conventional, regression-based estimation,
it can be directly substituted into existing experimental protocols without requiring other changes.
Our ultimate objective is to develop and validate a compressive sensing
data processing pipeline – culminating in an open-source software tool – that will allow for
efficient and accurate reconstruction of latent representations using data 
obtained via the reverse correlation method.

@@

\begin{figure}[h] % Figure at bottom of the page ([b] argument, could be "t" for top or "h" for here)
	\centering
	\includegraphics[width=\textwidth]{Figures/CompSensExamples.pdf}
	\caption{Compressive sensing (CS) delivers accurate signal reconstruction from sampling
	with a comparatively small number of samples.
	The latent representation in (\emph{A}) is estimated in (\emph{B-E}).
	In (\emph{B-C}) conventional regression-based estimation is used
	and in (\emph{D-E}) compressive sensing is used.
	The number of samples $n$ is displayed along with the correlation coefficient $r^2$
	between the estimated reconstruction and the original signal,
	as a measure of reconstruction quality.}
	\label{fig:csexample}
\end{figure}

@@

We will perform a quantitative analysis based on latent variable analysis methods.
Latent variable methods relate observed variation (\eg in tinnitus representations)
to latent variables that capture the observed variation (\eg major variation types across tinnitus percepts).
We will use principle component analysis (PCA), t-stochastic neighbor embedding (t-SNE; \cite{vandermaatenBarnesHutSNE2013}),
and uniform manifold approximation and projection (UMAP; \cite{mcinnesUMAPUniformManifold2020}).
Applying these dimensionality-reduction algorithms to a collection of representations
will identify major modes of variation across those representations,
uncovering latent similarities between representations.
Clusters of data points become readily visible in the lower-dimensional manifold generated
by these unsupervised machine learning methods, each of which represents
a data-driven tinnitus subtype (\autoref{fig:dimredexample}).
We will characterize these subtypes, identifying their properties and assigning them descriptive names.
In the case of PCA and UMAP, new data can be mapped into the lower-dimensional manifold,
allowing representations from new subjects to be classified into these subtypes.

\begin{figure}[h] % Figure at bottom of the page ([b] argument, could be "t" for top or "h" for here)
	\centering
	\includegraphics[width=0.8\textwidth]{Figures/umap.png}
	\caption{Tinnitus representations with different spectral characteristics cluster in a lower dimensional manifold.
	Tinnitus representation waveforms were generated using examples from the American Tinnitus Association website with added Gaussian noise.
	(\emph{a}) shows the frequency spectra for representative waveforms. In (\emph{b}), the waveforms
	are dimensonally-reduced using UMAP from 8,193 dimensions to 2.
	The waveforms cluster in this lower dimensional, revealing latent similarities.}
	\label{fig:dimredexample}
\end{figure}

\paragraph{Improving stimuli generation through data-driven distributions}

In Aim \#1, we generate stimuli by randomly sampling Fourier coefficients from a flat distribution to generate a spectrum.
We enforce minimal constraints on the stimuli (\eg that the frequency content is audible).
This has the benefit of reducing bias in the reconstructed representations,
but results in experiments that take longer to converge to a good reconstruction.
Previous studies using reverse correlation have attempted to reduce noise in the reconstructed representation
(and thus converge much faster) by carefully selecting stimuli biased towards a certain representation.
For example, Smith and colleagues \cite{smithMeasuringInternalRepresentations2012}
devised a task to uncover cognitive representations of faces using reverse correlation,
using pictures of human faces distorted by noise as stimuli for the task.
While this allowed the experimenters to perform fewer trials to achieve good reconstructions,
it introduced bias of what experimenters think human faces look like (by selecting the pictures),
defeating one of the main advantages of reverse correlation.

We propose to improve stimuli generation by exploiting our data from subsequent experiments.
Each putative reconstruction that we uncover leads to a new known data point hypothesized to lie on the manifold
of tinnitus representations.
We can treat this manifold much like a distribution and sample our stimuli from it,
resulting in stimuli that sound ``less random'' and more like actual tinnitus percepts.
This closed-loop experimental protocol means that our stimuli generation becomes more tinnitus-like
with every reconstruction, without introducing experimenter bias \emph{a priori}.

We will implement a variational autoencoder (VAE), a type of unsupervised machine learning model
that learns a latent representation of data as well as how to generate new data
that appears similar to data the model has been presented with before.
A VAE consists of an encoder artificial neural network
which constructs a latent representation
as a zero-mean, unit-variance normal-distributed vector
and a decoder artificial neural network
that reconstructs the input (\autoref{fig:vae}).
By training the VAE on reconstructed representations,
forcing the encoder to create a latent representation
and the decoder to reproduce the input from the latent representation,
the model will learn the manifold of tinnitus percepts.
By sampling the latent vector,
we can generate new stimuli informed by the representations the model has learned.
One limitation of VAEs is that sampling from the latent vector
tends to produce new data points that appear noisy.
In our experiment, this is a benefit,
as noisy, random stimuli is crucial to reverse correlation.
Through this generative model,
we will create stimuli that appear closer to actual tinnitus percepts
by learning directly from the data
without introducing external experimenter bias.

\begin{figure}[h] % Figure at bottom of the page ([b] argument, could be "t" for top or "h" for here)
	\centering
	\includegraphics[width=0.8\textwidth]{Figures/variational-autoencoder.png}
	\caption{Diagram of a variational autoencoder (VAE) learning a representation of the digit ``2''.
	VAEs assume that the data, $x$, are generated by a directed graphical model, $p_\theta(x|z)$,
	and that the encoder is learning an approximation $q_\phi(z|x)$, where $\phi$ and $\theta$
	denote the parameters of encoder and decoder respectively.
	The latent representation, $z$, is interpreted as originating from a multivariate Gaussian distribution.
	By sampling from the latent distribution, new data can be generated. Figure from \cite{IntroductionAutoencoders2020}.}
	\label{fig:vae}
\end{figure}
